Title

### 2011-09-30 inc/ms_model/ms_model.tex
Expanded on the nature of distribution functions

For a classical set of $N$ particles (labelled by the index $i$), distributed 6D space (3 position, 3 momentum) by 
\begin{gather}
  f_{\smallD}(\vec{r}, \vec{p}; t) = 
  \sum\limits^{N}_{i=1} \delta(\vec{r}_{i} - \vec{r}) \delta(\vec{p}_{i} - \vec{p}) \\
  \text{which satisfies} \quad \int d^{3}x\,d^{3}p \; f_{\smallD}(\vec{r}, \vec{p}; t) = N
\end{gather}
of mass $m$ which interact with some potential $V(\vec{r}_{i} - \vec{r}_{j})$, their motion is governed by the equations
\begin{subequations}\label{eq:std_motion}
\begin{gather}
  \frac{d\vec{r}_{i}(t)}{dt} = \frac{\vec{p}_{i}(t)}{m}\\
  \frac{d\vec{p}_{i}(t)}{dt} = -\sum\limits_{j} \frac{d}{d\vec{r}_{i}} V(\vec{r}_{i} - \vec{r}_{j})
\end{gather}
\end{subequations}
Now consider the time evolution of $f_{\smallD}$
\begin{equation}
  \frac{\partial f_{\smallD}}{\partial t} = 
  \frac{d\vec{r}}{dt} \frac{\partial f_{\smallD}}{\partial \vec{r}} 
  + \frac{\partial f_{\smallD}}{\partial \vec{p}} \frac{d\vec{p}}{dt}
\end{equation}
but with \ref{eq:std_motion} the final discreet evolution equation is
%TODO find missing minus sign!
\begin{equation}
  \frac{d}{dt} f_{\smallD}(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f_{\smallD}(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f_{\smallD} (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f_{\smallD}(\vecprime{r},\vecprime{p};t)
\end{equation}
%TODO ensemble av and mean-field
Final equation:
\begin{equation} \label{eq:formal_evolution}
  \frac{d}{dt} f(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f(\vecprime{r},\vecprime{p};t)
\end{equation}

>>>>

Before one may describe the evolution of a pulse of electrons, one must first learn to describe the pulse.
Rather than record the position of each electron, commonly one writes a distribution function for the electrons.
A distribution function describes the location of a number of objects in a certain space.
This space may be a 1D line, a 3D space, or even a 6D phase space (three spatial dimensions and three momentum dimensions).
The functional form may be chosen to appropriately characterize the objects in a natural way, however one property is true for all distribution functions: when integrated over all relevant space, all objects should be accounted for.
In $n$ dimensional space, with $N$ objects, this normalization condition on a distribution function $f$ can be written mathematically as
\begin{equation}
N = \int\limits_{\text{all space}} \!\!\! f(\vec{x}) \; d^{n}x
\end{equation}
which for 6D phase space is written as
\begin{equation} \label{eq:normalization}
n = \int f_{\smallD}(\vec{r}, \vec{p}; t) \; d^{3}x\,d^{3}p
\end{equation}
This notation suggests to the reader that the distribution function is implicitly a function of time as well as of the spatial and momentum dimensions.

For a classical set of $N$ particles (labelled by the index $i$), distributed in 6D space (3 position, 3 momentum) by 
\begin{equation}
  f_{\smallD}(\vec{r}, \vec{p}; t) = 
  \sum\limits^{N}_{i=1} \delta(\vec{r}_{i} - \vec{r}) \delta(\vec{p}_{i} - \vec{p})
\end{equation}
which automatically satisfies \ref{eq:normalization}.
The particles have mass $m$ which interact with some potential $V(\vec{r}_{i} - \vec{r}_{j})$, their motion is governed by the equations
\begin{subequations}\label{eq:std_motion}
\begin{gather}
  \frac{d\vec{r}_{i}(t)}{dt} = \frac{\vec{p}_{i}(t)}{m}\\
  \frac{d\vec{p}_{i}(t)}{dt} = -\sum\limits_{j} \frac{d}{d\vec{r}_{i}} V(\vec{r}_{i} - \vec{r}_{j})
\end{gather}
\end{subequations}
Now consider the time evolution of $f_{\smallD}$
\begin{equation}
  \frac{\partial f_{\smallD}}{\partial t} = 
  \frac{d\vec{r}}{dt} \frac{\partial f_{\smallD}}{\partial \vec{r}} 
  + \frac{\partial f_{\smallD}}{\partial \vec{p}} \frac{d\vec{p}}{dt}
\end{equation}
but with \ref{eq:std_motion} the final discreet evolution equation is
%TODO find missing minus sign!
\begin{equation}
  \frac{d}{dt} f_{\smallD}(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f_{\smallD}(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f_{\smallD} (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f_{\smallD}(\vecprime{r},\vecprime{p};t)
\end{equation}
%TODO ensemble av and mean-field
Final equation:
\begin{equation} \label{eq:formal_evolution}
  \frac{d}{dt} f(\vec{r}, \vec{p}; t) =
  -\frac{\vec{p}}{m} \frac{\partial}{\partial \vec{r}} f(\vec{r}, \vec{p}; t)
  + \frac{\partial}{\partial \vec{p}} f (\vec{r}, \vec{p}; t)
  \frac{\partial}{\partial \vec{r}} \iint d\vecprime{r} d\vecprime{p} V(\vec{r} - \vecprime{r}) f(\vecprime{r},\vecprime{p};t)
\end{equation}
